---
name: Jun-I Wu
position: "Regulatory Affairs Specialist"
aboutme: Regulatory affairs specialist for medical devices including IVD and IVD data analysis
address: "Zhubei City, Hsinchu County, Taiwan"
#phone: 
email: "jimewu@gmail.com"
github: jimewu/ivd-ep-toolkit-2021
linkedin: jimewu
#headcolor: 414141
headcolor: CB4042
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    latex_engine: "xelatex"
    includes:
        in_header: toolkit/preamble.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    warning = FALSE,
    message = FALSE
)
```

```{r load_pkg, include=FALSE}
pkg_lst <- c(
    "knitr",
    "dplyr",
    "glue",
    "readr",
    "scales"
)

lapply(pkg_lst, function(pkg) {
    if (system.file(package = pkg) == "") install.packages(pkg)
})

lapply(
    pkg_lst,
    library,
    character.only = TRUE
)
```

# Experience
**<span style="font-size:1em;">AlfaBeta CRO Ltd.</span>** \hfill _Zhubei City, Taiwan_  
Regulatory Affairs Specialist \hfill _Jan. 2020 - Present_  

- Provide lectures of IVD pre-clinical tests (CLSI ep5, 6, 7, 9, 17, 25)

- IVD pre-clinical test planning, *[data analysis using R](https://github.com/jimewu/ivd-ep-toolkit-2021)*, and report (ELISA, strip, molecular test and analyzer)

- FDA Q-submission (Oral Cancer IVD and IVD for chronic kidney disease), Registration of Class I device (Spectrophotometer), EUA sbumission (Ventilator)

- TFDA QSD translation and submission (Electrosurgical cutting and coagulation device), device registration (Manual surgical instruments)

- EU Clinical evaluation report writing including LSR (Blood pressure measuring system, Extra-oral source X-ray System, Medical displays, thermometers, contact lenses, Intermittent pneumatic compression device and sequential compression device), self-declaration of conformity of general IVD (Spectrophotometer)

- Clinical trial planning, submission, and GCP activities and documentation (retrospective for oral cancer IVD, prospective for mobile X-ray system)

**<span style="font-size:1em;">China Medical University Hospital</span>** \hfill _Zhunan County, Taiwan_  
IVD Biomarker Project Research Associate \hfill _Jan. 2017 - 2018_  

- Discovery and validation of blood biomarker for earlier stage lung cancer

# Publications

- Lin, Yi-Pei, **Jun-I. Wu**, Chien-Wei Tseng, Huei-Jane Chen, and Lu-Hai Wang. 2019. “Gjb4 Serves as a Novel Biomarker for Lung Cancer and Promotes Metastasis and Chemoresistance via Src Activation.” Oncogene 38 (6): 822–37.

- **Wu, Jun-I**, Yi-Pei Lin, Chien-Wei Tseng, Hui-Jane Chen, and Lu-Hai Wang. 2019. “Crabp2 Promotes Metastasis of Lung Cancer Cells via HuR and Integrin Β1/FAK/ERK Signaling.” Scientific Reports 9 (1): 845. 
 
# Education

**<span style="font-size:1em;">National Central University</span>** \hfill _Chungli County, Taiwan_  
Ph.D. in Molecular Medicine \hfill _2019_

**<span style="font-size:1em;">National Cheng Kung University</span>** \hfill _Tainan City, Taiwan_  
MS. in Biochemistry and Molecular Biology \hfill _2008_

# Certificate and Skills

TOEIC (955), IVD preclinical data analysis (R), parametized reproducible report making (RMarkdown & officeverse), bash. Adept user of Linux.